Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-22 Papers/ms.tex
Paragraph and caption

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures2.pdf}
\caption{\label{fig:substructures2}}
\end{center}
\end{figure}

>>>>

Despite weak evidence for the existence of substructure, when we examine the
expected value of the empirical measure of substructure positions
(Figure~\ref{fig:substructures2}) we find no consistency in their positions,
unlike for the simulated data (Figure~\ref{fig:substructures}). This situation
is not uncommon. For example, \citet{exoplanet} found evidence for a large
number of Keplerian signals in a time series, but the number of such signals
with well constrained properties was much lower.

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{substructures2.pdf}
\caption{The positions of substructures encountered in the MCMC sampling
for the Cosmic Horseshoe; technically a Monte Carlo approximation to the
posterior expected value of the empirical measure of substructure
positions. Unlike Figure~\ref{fig:substructures}, for the Cosmic Horseshoe
there is little consistency in the positions of the substructures.
\label{fig:substructures2}}
\end{center}
\end{figure}
